Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-04 popl24/scratch.tex
checkpoint

\begin{proof}
  Let $\prog$ be as defined in Definition \ref{definition-gmwgate-certification}.
  We observe:
  $$
  {\footnotesize
    \begin{array}{c}
      \prog_2 = \\
      \prog[\ttt{v[1,g1out]}/\ttt{flip[1,s11]}][\ttt{v[2,g1out]}/\ttt{flip[2,s12]}][\ttt{v[1,g2out]}/\ttt{flip[1,s21]}][\ttt{v[2,g2out]}/\ttt{flip[2,s22]}]
    \end{array}
  }
  $$ Now, the assumption of well-typedness of
  $\prog_1;E[\mathit{gate}(\ttt{g},v_1,v_2)]$ assures that $\ttt{g}$
  has not been previously used as a gate identifier in $\prog_1$,
  since otherwise the views $\ttt{v[1,gout]}$ and $\ttt{v[2,gout]}$
  would have been previously defined. This ensures $\vars(\prog_1,x)
  \cap \vars(\prog_2) = \varnothing$ for:
  $$x \in \{ \ttt{v[1,g1out]}, \ttt{v[2,g1out]}, \ttt{v[1,g2out]}, \ttt{v[2,g2out]}\}$$
  given condition (iii) in Definition \ref{definition-gmwgate-certification}.
  Thus by Lemma \ref{lemma-substitution} we have:
  $$\sep{\progtt(\prog_1;\prog_2)}{\ttt{\{v[1,g1out],v[1,g2out]\}}}{\ttt{\{v[2,gout]\}}}$$
  and
  $$\sep{\progtt(\prog_1;\prog_2)}{\ttt{\{v[2,g1out],v[2,g2out]\}}}{\ttt{\{v[1,gout]\}}}$$
  Since $\vars(\prog_1) \cap \vars(\prog_2)$ are only the wire inputs to $\ttt{g}$,
  therefore by assumption and Lemma \ref{lemma-gmw-frame}:
  $$\sep{\progtt(\prog_1;\prog_2)}{(S_{\{1\}} \cup V_{\{1\}})}{\ttt{\{v[2,gout]\}}}$$
  and also:
  $$\sep{\progtt(\prog_1;\prog_2)}{\ttt{\{v[1,g1out],v[1,g2out]\}}}{(S_{\{2\}}\cup V_{\{2\}})}$$
  etc., so the result follows. 
\end{proof}

>>>>

\begin{proof}
  Let $\prog$ be as defined in Definition \ref{definition-gmwgate-certification}.
  We observe:
  $$
  {\footnotesize
    \begin{array}{c}
      \prog_2 = \\
      \prog[\ttt{v[1,g1out]}/\ttt{flip[1,s11]}][\ttt{v[2,g1out]}/\ttt{flip[2,s12]}][\ttt{v[1,g2out]}/\ttt{flip[1,s21]}][\ttt{v[2,g2out]}/\ttt{flip[2,s22]}]
    \end{array}
  }
  $$ Now, the assumption of well-typedness of
  $\prog_1;E[\mathit{gate}(\ttt{g},v_1,v_2)]$ assures that $\ttt{g}$
  has not been previously used as a gate identifier in $\prog_1$,
  since otherwise the views $\ttt{v[1,gout]}$ and $\ttt{v[2,gout]}$
  would have been previously defined. This ensures $\vars(\prog_1,x)
  \cap \vars(\prog_2) = \varnothing$ for:
  $$x \in \{ \ttt{v[1,g1out]}, \ttt{v[2,g1out]}, \ttt{v[1,g2out]}, \ttt{v[2,g2out]}\}$$
  given condition (iii) in Definition \ref{definition-gmwgate-certification}.
  Thus by Lemma \ref{lemma-substitution} we have:
  $$\sep{\progtt(\prog_1;\prog_2)}{\ttt{\{v[1,g1out],v[1,g2out]\}}}{\ttt{\{v[2,gout]\}}}$$
  and
  $$\sep{\progtt(\prog_1;\prog_2)}{\ttt{\{v[2,g1out],v[2,g2out]\}}}{\ttt{\{v[1,gout]\}}}$$
  Since $\vars(\prog_1) \cap \vars(\prog_2)$ are only the wire inputs to $\ttt{g}$,
  therefore by assumption and Lemma \ref{lemma-gmw-frame} the following assertions are
  valid:
  \begin{mathpar}
    \sep{\progtt(\prog_1;\prog_2)}{(S_{\{1\}} \cup V_{\{1\}})}{\ttt{\{v[2,gout]\}}}

    \sep{\progtt(\prog_1;\prog_2)}{\ttt{\{v[1,g1out],v[1,g2out]\}}}{(S_{\{2\}}\cup V_{\{2\}})}

    \sep{\progtt(\prog_1;\prog_2)}{(S_{\{2\}} \cup V_{\{2\}})}{\ttt{\{v[1,gout]\}}}

    \sep{\progtt(\prog_1;\prog_2)}{\ttt{\{v[2,g1out],v[2,g2out]\}}}{(S_{\{1\}}\cup V_{\{1\}})}
  \end{mathpar}
  The result follows by Lemma \ref{lemma-separation}.
\end{proof}
